\LARGE \bf IMU-based pose-estimation for spherical robots with limited resources

### 2021-05-24 mfi21/ieeeconf/root.tex
changed one comma

\subsection{Orientation}
A first experiment is performed to show the overall performance of the Autogain computation for the orientation. The IMU was manually rotated in arbitrary directions, and the orientation plotted using the Madgwick filter and the Autogain filter.
As expected, the overall behavior of the presented algorithm and the Madgwick filter is very similar in the dynamic case, as shown in Figure \ref{quaternion1}.
\begin{figure}
\includegraphics[width=\linewidth]{./graphics/AutoVsMad.eps}
\caption{Quaternion-values of the presented fusion of complementary and Madgwick filter and only the Madgwick filter}
\label{quaternion1}
\end{figure}
Therefore the more expressive part is the change between motion and standstill, as in motion, both filters use the same algorithm but differ during standstill and slow motion.
As described in Section \ref{sec:SOA}, the Madgwick filter has a rather strong jitter during slow movements and standstill. 
To evaluate specifically the change between slow motion and standstill, a further experiment is performed.
Figure \ref{distance} show the distance to a precise external reference over a short excerpt of the experiment with three phases of slow motion and rotation at second 7, 9 and 11. 
For external reference, we used a precise optical tracking system. 
The definition and proposed calculation of the distance of 2 quaternions of \cite{kuffner} was used.
It describes the direct angle between both quaternions,
The optical system matches the overall orientation of both IMU-based algorithms quite well and lacks the perturbations of the pure Madgwick filter.
The transformation of the orientation by the optical tracking system and the IMU-based algorithms yield two unknown transformations, the relative orientation of the coordinate system of IMU to optical coordinate system and how the axes are interpreted on the tracked structure itself.
Therefore, the algorithm proposed in \cite{dornaika} was used to solve these two unknown transformations on basis of the resulting data, to match the orientations of optical and IMU-based data.
As this matching of the optical system happens on basis of one of the two IMU orientation data-sets, the comparison of absolute differences may be misleading, as the transformations were matched on basis of the autogain filter. 
To stress the jitter behavior of the Madgwick without relying on absolute orientation, which will be part of further research, Figure \ref{diffdistance} shows the derivative of the distance.
Here the change of direction due to small oscillations and the smoother fusion algorithm in comparison to the tracking is even more apparent.

>>>>

\subsection{Orientation}
A first experiment is performed to show the overall performance of the Autogain computation for the orientation. The IMU was manually rotated in arbitrary directions, and the orientation plotted using the Madgwick filter and the Autogain filter.
As expected, the overall behavior of the presented algorithm and the Madgwick filter is very similar in the dynamic case, as shown in Figure \ref{quaternion1}.
\begin{figure}
\includegraphics[width=\linewidth]{./graphics/AutoVsMad.eps}
\caption{Quaternion-values of the presented fusion of complementary and Madgwick filter and only the Madgwick filter}
\label{quaternion1}
\end{figure}
Therefore the more expressive part is the change between motion and standstill, as in motion, both filters use the same algorithm but differ during standstill and slow motion.
As described in Section \ref{sec:SOA}, the Madgwick filter has a rather strong jitter during slow movements and standstill. 
To evaluate specifically the change between slow motion and standstill, a further experiment is performed.
Figure \ref{distance} show the distance to a precise external reference over a short excerpt of the experiment with three phases of slow motion and rotation at second 7, 9 and 11. 
For external reference, we used a precise optical tracking system. 
The definition and proposed calculation of the distance of 2 quaternions of \cite{kuffner} was used.
It describes the direct angle between two quaternions.
The optical system matches the overall orientation of both IMU-based algorithms quite well and lacks the perturbations of the pure Madgwick filter.
The transformation of the orientation by the optical tracking system and the IMU-based algorithms yield two unknown transformations, the relative orientation of the coordinate system of IMU to optical coordinate system and how the axes are interpreted on the tracked structure itself.
Therefore, the algorithm proposed in \cite{dornaika} was used to solve these two unknown transformations on basis of the resulting data, to match the orientations of optical and IMU-based data.
As this matching of the optical system happens on basis of one of the two IMU orientation data-sets, the comparison of absolute differences may be misleading, as the transformations were matched on basis of the autogain filter. 
To stress the jitter behavior of the Madgwick without relying on absolute orientation, which will be part of further research, Figure \ref{diffdistance} shows the derivative of the distance.
Here the change of direction due to small oscillations and the smoother fusion algorithm in comparison to the tracking is even more apparent.
